An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-15 EconGrowth2.Rnw
energyType=NA is no longer accepted. Use energyType="none".

<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters. $\\gamma$ is always 0.0, because energy is not included in this model.">>=
cdResampleTrianglePlot(energyType=NA)
@

@@

<<CES_lambda_gamma_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType=NA)
@

<<CES_sigma_1_delta_1_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType=NA)
@

@@

<<CD_Params_Table, results='asis'>>=
printCDParamsTable(energyType=NA)    #Without energy
@

@@

<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCDParamsGraph(energyType=NA)
@

@@

<<CES_Params_Table, results='asis'>>=
printCESParamsTableA(energyType=NA)
printCESParamsTableB(energyType=NA)
@

<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType=NA)
@

>>>>

<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters. $\\gamma$ is always 0.0, because energy is not included in this model.">>=
cdResampleTrianglePlot(energyType="none")
@

@@

<<CES_lambda_gamma_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="none")
@

<<CES_sigma_1_delta_1_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="none")
@

@@

<<CD_Params_Table, results='asis'>>=
printCDParamsTable(energyType="none")    #Without energy
@

@@

<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCDParamsGraph(energyType="none")
@

@@

<<CES_Params_Table, results='asis'>>=
printCESParamsTableA(energyType="none")
printCESParamsTableB(energyType="none")
@

<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="none")
@
